SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
barriers

Rosen \cite{rosen1988global} also introduced moving computations from successors
but using value numbering. Their algorithm iterates on computations of same rank
and move the code with identical computations from the sibling branch to a
common dominator if they are very busy \cite{steven1997advanced}. We also
incorporate ranking of expressions in our implementation.

@@

>>>>

Rosen \cite{rosen1988global} also introduced moving computations from successors
but using value numbering. Their algorithm iterates on computations of same rank
and move the code with identical computations from the sibling branch to a
common dominator if they are very busy \cite{steven1997advanced}.

@@

Barriers are based on the concept of pinned instructions \cite{click1995global}
but extended to adapt to LLVM IR. Since a basic block in LLVM IR is actually an
extended basic block because there might be calls in the middle of a basic block
which might not return. So barriers can be present in the middle of a basic
block. Essentially, any instruction that cannot not guarantee progress is marked
as a barrier. In the absense of context (as in our current implementation), some
instructions which might be safe are still classified a barrier e.g., volatile
loads/stores, calls with missing attributes.
